### 2017-11-27 Chapter3/introduction.tex
Latest on 27/11/2017

    The rest of the chapter is organized as follows. We elaborate our contributions in section~\ref{sec:contri} and in section~\ref{sec:eucbv} we present the  EUCBV algorithm. Our main theoretical results are stated in section~\ref{sec:results}, while the proofs are established in section \ref{sec:proofTheorem}. Section~\ref{sec:expt} contains results and discussions from our numerical experiments. We draw our conclusions in section \ref{sec:conc} and Appendix \ref{sec:app:EUCBV} contains the proofs of the lemmas that have been used for proving the main result.

>>>>

    The rest of the chapter is organized as follows. We elaborate our contributions in section~\ref{sec:contri} and in section~\ref{sec:eucbv} we present the  EUCBV algorithm. Our main theoretical results are stated in section~\ref{sec:results}, while the proofs are established in section \ref{sec:proofTheorem}. Section~\ref{sec:expt} contains results and discussions from our numerical experiments. We summarize in section \ref{sec:conc} and Appendix \ref{sec:app:EUCBV} contains the proofs of the lemmas that have been used for proving the main result.

### 2017-11-27 Chapter4/intro.tex
Latest on 27/11/2017

	The rest of the chapter is organized as follows. We specify all the notations and assumptions in section~\ref{tbandit:notations}. Then we define the problem statement for the TBP setting in section~\ref{tbandit:probDef}. In the next section~\ref{tbandit:motivation} we discuss the motivations behind the TBP setting. In section~\ref{tbandit:prevRes} we discuss extensively on the various state-of-the-art algorithms available for the pure exploration setting and then in section~\ref{tbandit:prevResAPT} we discuss the latest works done in the TBP setting. Finally, we draw our conclusions in section \ref{tbandit:conc}.

>>>>

	The rest of the chapter is organized as follows. We specify all the notations and assumptions in section~\ref{tbandit:notations}. Then we define the problem statement for the TBP setting in section~\ref{tbandit:probDef}. In the next section~\ref{tbandit:motivation} we discuss the motivations behind the TBP setting. In section~\ref{tbandit:prevRes} we discuss extensively on the various state-of-the-art algorithms available for the pure exploration setting, in section~\ref{tbandit:connection} we draw the connection between pure exploration and thresholding bandit setting and then in section~\ref{tbandit:prevResAPT} we discuss the latest works done in the TBP setting. Finally, we summarize in section \ref{tbandit:conc}.
